### 2021-08-18 sections/appendix/blocking_time_formula/main.tex
Add extra checks (#12)
* Update environment to include proselint

* Add proselint check as a task

* Update CI to run proselint check

* Make changes suggested by proselint

* Fix typo in ci.yml

* Add alex to github actions checks

* Apply changes based on Alex's suggestions

* Include alex check as a task

* Apply alex's suggestion

The mean sojourn time for each state is given by the inverse of the out-flow of
that state ~\cite{Stewart2019}.
However, whenever a type 2 individual arrives at the system, no subsequent 
arrival of another type 2 individual can affect its pathway or total time in 
the system.
Therefore, looking at the mean time in the system from the perspective of an 
individual of the second type, all such type 2 arrivals need to be ignored.
Note here that this is not the case for individuals of the first type.
Whenever a type 2 individual is blocked and a type 1 individual arrives the type
2 individuals will remain blocked for some additional amount of time.
Thus, the mean time that a type 2 individual spends at each state is given by:

@@

Thus, having calculated the mean blocking time for all blocking states 
\(b(u,v)\), it only remains to put them together in a formula.
The resultant formula for the mean blocking time is given by:

>>>>

The mean sojourn time for each state is given by the inverse of the out-flow of
that state ~\cite{Stewart2019}.
However, whenever a type 2 individual arrives at the system, no subsequent 
arrival of another type 2 individual can affect its pathway or total time in 
the system.
Therefore, looking at the mean time in the system from the perspective of an 
individual of the second type, all such type 2 arrivals need to be ignored.
Note here that this is not the case for individuals of the first type.
Whenever a type 2 individual is blocked and a type 1 individual arrives the type
2 individuals will stay blocked for some additional amount of time.
Thus, the mean time that a type 2 individual spends at each state is given by:

@@

Thus, having calculated the mean blocking time for all blocking states 
\(b(u,v)\), they can be combined together in a formula.
The resultant formula for the mean blocking time is given by:
